Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
no need to cite Weber-Fechner

Taking the logarithm of a magnitude spectrum is ubiquitous in audio signal processing.
Indeed, it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure. \ja{Cite?}
We must also recall that the measured amplitude of sound sources often decays polynomially with the distance to the microphone, a source of spurious variability in scene classification.
Logarithmic compression can linearize this dependency, facilitating the construction of a powerful invariant at the classifier stage.

>>>>

Taking the logarithm of a magnitude spectrum is ubiquitous in audio signal processing.
Indeed, it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure.
We must also recall that the measured amplitude of sound sources often decays polynomially with the distance to the microphone, a source of spurious variability in scene classification.
Logarithmic compression can linearize this dependency, facilitating the construction of a powerful invariant at the classifier stage.
